Immune-Related Adverse Events (irAEs) associated with Immune Checkpoint Inhibitor (ICI) Therapy in Bladder Cancer: An Analysis of the FDA Adverse Event Reporting System (FAERS)

### 2025-04-04 products/manuscript/Manuscript.qmd
Part 4 of MADA Project

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

*Write a summary of your project.* *This part has not been completed. The source code has been left as is*

@@

*Bladder cancer is the ninth most common type of cancer, according to a 2022 report published by the International Agency for Research on Cancer [@Bray2024]. The American Cancer Society estimates approximately 85,000 new bladder cancer cases, and approximately 17,000 bladder cancer deaths in the United States in 2025.*

*The cancer is more common in males than in females, with a male:female ratio of about 4:1[@Leslie2025-lp]. Risk factors for bladder cancer include smoking and occupational chemical exposures (in particular, aromatic amines and polycyclic aromatic hydrocarbons). Certain dietary factors, impaired microbiome, and pelvic radiotherapy may also increase the risk of bladder cancer [@Jubber2023].*

*Treatment of bladder cancer is multifaceted and depends on the type of tumor. Surgical resection, adjuvant and intravesical chemotherapy, Bacillus Calmette–Guérin (BCG) immunotherapy, and systemic chemotherapy are the different treatment options available [@Leslie2025-lp].*

*According to the National comprehensive Cancer Network (NCCN) guidelines, immunotherapy with immune checkpoint inhibitors (ICIs) is recommended at various stages of bladder cancer treatment. ICIs such as pembrolizumab, atezolizumab, nivolumab, and avelumab are FDA approved and recommended for the adjuvant and first and second-line treatment of bladder cancer [@Flaig2024].*

*ICIs are associated with various adverse effects, particularly with immune-related adverse events (irAEs) such as pnemonitis, hepatitis, colitis, hypothyroidism, dermatitis, and others [@Yin2023].This study aims to analyze real-world adverse event data from the FDA Adverse Event Reporting System associated with ICI therapy in bladder cancer.*

@@

*The United States Food and Drug Administration (FDA) maintains a dashboard of adverse event reports in the FDA Adverse Event Reporting System (FAERS) [@us2018fda]. FAERS is a publicly available dashboard of safety reports submitted by patients, healthcare professionals, and pharmaceutical companies.*

*Since FAERS consists of self-reported data from multiple sources, there may be duplicates, missing data as well as various errors. The findings of this study should be considered in context of this data limitation.*

@@

*The study aims to analyze whether irAEs associated with ICIs generate a signal of disproportionate reporting (SDR). The goal is to determine whether irAEs associated with ICIs in baldder cancer are greater than expected, and thus further research and strategies to deal with these adverse events is required.*

@@

*Describe your methods. That should describe the data, the cleaning processes, and the analysis approaches. You might want to provide a shorter description here and all the details in the supplement.* *This part has not been completed. The source code has been left as is* *Details have been provided in the data acquisition and statistical analysis parts.*

@@

*In order to obtain the FAERS data, the ICIs were used to search by product. Pembrolizumab, atezolizumab, avelumab, and nivolumab were the keywords used. Previously, durvalumab, and ipilimumab were also approved for bladder cancer treatment. However, this indication has since then been removed by the manufacturers. As such, these were not considered. Following this, the search was limited to cases of bladder cancer. A total of 1,886 reactions were obtained.*

@@

*The file has been downloaded as an Excel file. The code for the analysis would involve loading the file, removing duplicates, assessing missing data, and deciding whether to remove it.* *This will be followed by filtering the data to retain only irAEs. While this step could be performed within the FAERS dashboard, this is not always a straightforward process. FAERS writes all the reactions associated with an agent in a single column, such that one column may have over 10-15 reactions. As such, this step will be performed here.*

*The FAERS data initially consisted of 2948 reactions associated with ICIs in bladder cancer.*

*Reactions with concomitant suspect products, combination products, and those which were not irAEs were removed. This resulted in a total of 369 cases. The details are available in the processing code file.*

@@

*The first of the analysis will consists of descriptive statistics. Continous variables will be summarized as means, whereas categorical variables will be summarized as counts and percenatges.*

*The second part of the analysis will involve a disproportionality analysis. This analysis uses the following formula to calculate the reported odds ratio (ROR).*

*a = irAES reported with ICIs* *b = irAEs reported with all other drugs* *c = All other AEs reported with ICIs* *d = All other AEs reported with other drugs*

*ROR = a/c / b/d*

*Other details in the analysis will be finalized later.*

@@

@tbl-summarytable *provides the patient characteristics, and summary of reactions by type of immune checkpoint inhibitor, and organ system affected.*

*The mean age reported was 66.94±17.65. A large percentage of the reactions occurred in males (70.2%). This may be because bladder cancer is much more common in males than in females.*

*Over 60% of the reactions were associated with pembrolizumab. A majority of the reactions were serious (83.7%)*

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Table 1: Descriptive Statistics"
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

@@

*@fig-result shows the number of reactions by drug, along with the seriousness of the reaction.*

```{r}
#| label: fig-result
#| fig-cap: "Bar chart of outcome of immune checkpoint inhibitors"
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure1.png"))
```

*@fig-result1 shows the bar chart by type of organ system involved in the reaction.*

```{r}
#| label: fig-result1
#| fig-cap: "Bar chart of types of reactions"
#| echo: FALSE
knitr::include_graphics(here("results","figures","figure2.png"))
```

@@

*This part has not yet been edited.*

*Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here.*

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

@@

*Summarize what you did, what you found and what it means.*

@@

*Discuss what you perceive as strengths and limitations of your analysis.*

@@

*What are the main take-home messages?*

*Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end*

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like.

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(huxtable)
library(knitr)
```

@@

Background: Bladder cancer is the ninth most common type of cancer worldwide. Treatment options include surgery, chemotherapy and immunotherapy. Immune checkpoint inhibitors (ICIs) are a class of immunotherapeutic agents recommended for the treatment of bladder cancer. ICIs have been associated with certain immune-related adverse events (irAEs)

Methods: Reports in the FAERS dashbaord through December 2024 were analyzed for irAEs to four ICIs recommended in bladder cancer - atezolizumab, avelumab, nivolumab, and pembrolizumab. Standardized queries were used to identify cases of rash, pruritus, hypothyroidism, hyperthyroidism, colitis, hepatitis, and nephritis. Descriptive and disproportionality analyses were performed to detect safety signals.

Results: Out of 2948 cases identified from FAERS, 365 cases with irAEs were analyzed. The largest number of cases were reported for pembrolizumab (n=307), followed by atezolizumab (n = 91), avelumab (n = 41), and nivolumab (n =37). Pembrolizumab was found to have safety signals for all irAEs considered together (PRR: 1.8 (1.52, 2.14), ROR: 2.07 (1.69, 2.55), IC:	0.36 (0.29, 0.44)). A safety signal was also found for rash (PRR: 2.11 (1.17, 3.8), ROR:	2.14 (1.18, 3.9), IC:	0.44 (0.17, 0.71)). Safety signals for atezolizumab included hyperthyroidism and nephritis, while hypothyroidism was identified as a concern for avelumab.

Conclusion: Immune-related adverse events are found to be associated with immune checkpoint inhibitor therapy in bladder cancer. Pembrolizumab appears to have the highest risk, though this may be due to its early approval (2014). Appropriate treatment guidelines must be developed to address the management of irAEs associated with ICI therapy in bladder cancer.

@@

Bladder cancer is the ninth most common type of cancer, according to a 2022 report published by the International Agency for Research on Cancer [@Bray2024]. The American Cancer Society estimates approximately 85,000 new bladder cancer cases, and approximately 17,000 bladder cancer deaths in the United States in 2025.

The cancer is more common in males than in females, with a male-female ratio of about 4:1[@Leslie2025-lp]. Risk factors for bladder cancer include smoking and occupational chemical exposures (in particular, aromatic amines and polycyclic aromatic hydrocarbons). Certain dietary factors, impaired microbiome, and pelvic radiotherapy may also increase the risk of bladder cancer [@Jubber2023].

Treatment of bladder cancer is multifaceted and depends on the type of tumor. Surgical resection, adjuvant and intravesical chemotherapy, Bacillus Calmette–Guérin (BCG) immunotherapy, and systemic chemotherapy are the different treatment options available [@Leslie2025-lp].

According to the National Comprehensive Cancer Network (NCCN) guidelines, immunotherapy with immune checkpoint inhibitors (ICIs) is recommended at various stages of bladder cancer treatment. ICIs such as pembrolizumab, atezolizumab, nivolumab, and avelumab are FDA approved and recommended for the adjuvant and first and second-line treatment of bladder cancer [@Flaig2024].

ICIs are associated with various adverse effects, particularly with immune-related adverse events (irAEs) such as pneumonitis, hepatitis, colitis, hypothyroidism, dermatitis, and others [@Yin2023].This study aims to analyze real-world adverse event data from the FDA Adverse Event Reporting System associated with ICI therapy in bladder cancer.

@@

The United States Food and Drug Administration (FDA) maintains a dashboard of adverse event reports in the FDA Adverse Event Reporting System (FAERS) [@us2018fda]. FAERS is a publicly available dashboard of safety reports submitted by patients, healthcare professionals, and pharmaceutical companies.

Since FAERS consists of self-reported data from multiple sources, there may be duplicates, missing data as well as various errors. The findings of this study should be considered in context of this data limitation.

@@

The study aims to analyze whether irAEs associated with ICIs generate a signal of disproportionate reporting (SDR). The goal is to determine whether irAEs associated with ICIs in baldder cancer are greater than expected, and thus further research and strategies to deal with these adverse events is required.

@@

The FAERS dashboard was searched by product to obtain cases related to the use of ICIs in bladder cancer. This data was then filtered to retain only irAE cases. Other adverse events and duplicate cases were removed. Following this, the demographic and drug characteristics were summarized.

To assess whether an ICI has a safety signal associated with a particular irAE, three metrics were used:
1. Proportional reporting ratio (PRR):
This approach compares the proportion of reports for a specific adverse event with a drug of interest to the proportion of the same event reported for all other drugs.

2. Reporting odds ratio (ROR):
This metric is obtained by comparing the ratio of a drug's adverse event reports to all other reports for that drug against the same ratio across all drugs.

3. Information component (IC):
For this metric, the observed vs. expected reporting of a drug-adverse event combination is compared.

A random forest model was fit to distinguish between serious and non-serious cases on the basis of age, sex, and ICI.

@@

In order to obtain the FAERS data, the ICIs were used to search by product. Pembrolizumab, atezolizumab, avelumab, and nivolumab were the keywords used. Previously, durvalumab, and ipilimumab were also approved for bladder cancer treatment. However, this indication has since then been removed by the manufacturers. As such, these were not considered. Following this, the search was limited to cases of bladder cancer. A total of 2948 reactions were obtained.

@@

The file was downloaded as an Excel file. First, the column were renamed so as to make them easier to use in code. Then, products with concomitant drugs were removed, so as to focus only on cases associated with ICIs. Then, cases which also had other drugs as the suspect active ingredients were removed. 
This was followed by retaining only the irAEs.
A list of common irAEs was used. This list is available in the supplementary material. Any reactions which had the same age, weight, FDA received date, country of occurrence, suspected active ingredient, and reported reaction were considered duplicates and were removed.
Following this, the reactions were coded according to the MedDRA Preferred Terms (PTs), and classified according to the System Organ Class (SOC).
The age values were converted to numeric and the countries were re-classified as US, outside US, and not specified.
The code for the analysis would involve loading the file, removing duplicates, assessing missing data, and deciding whether to remove it. The details are available in the processing code file.

The processing was done according to @fig-processing1.

```{r}
#| label: fig-processing1
#| fig-cap: "Study Flowchart"
#| echo: FALSE
knitr::include_graphics(here("assets","Figure1.png"))
```

@@

Firstly, descriptive statistics were used to describe the demographic and other characteristics.
This was followed by creating some descriptive figures.
The PRR, ROR and IC (along with their 95% CI) were then calculated to assess the drug signal.
A random forest model was built using age, sex, and ICI, to distinguish between serious and non-serious cases.

@@

@tbl-summarytable provides the patient characteristics, and summary of reactions by type of immune checkpoint inhibitor, and organ system affected.

The mean age reported was 66.94±17.65. A large percentage of the reactions occurred in males (70.2%). This may be because bladder cancer is much more common in males than in females.

Over 60% of the reactions were associated with pembrolizumab. A majority of the reactions were serious (83.7%).

Most of the reaction were reported by healthcare professionals. Since FAERS is a US-based dashboard, many reactions were reported from the US.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Descriptive Statistics"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)

# Load and modify table (all processing hidden)
demographic_stats <- readRDS(here::here("results", "tables", "summarytable.rds"))[-c(1, 2), ]

# Create and format flextable (visible in output only)
desc_stats_table <- flextable(demographic_stats) |> 
  # Borders
  border_outer(part = "all") |> 
  border_inner(part = "all") |> 
  # Formatting
  bold(part = "header") |> 
  fontsize(size = 10, part = "all") |> 
  color(color = "black", part = "all") |> 
  # Layout
  set_table_properties(width = 1, layout = "autofit") |>  # Full width
  align(align = "center", part = "header") |> 
  padding(padding = 4, part = "all")

# Display table
desc_stats_table
```

@@

@tbl-summarytable1 shows the number of reactions by organ system and the ICI.

```{r}
#| label: tbl-summarytable1
#| tbl-cap: "Reactions by Organ System and Drug"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(here)

# Load and prepare data
resulttable1 <- readRDS(here("results", "tables", "summarytable1.rds"))
resulttable1_df <- as.data.frame(resulttable1)
colnames(resulttable1_df) <- as.character(resulttable1_df[1,])
resulttable1_df <- resulttable1_df[-1,]

# Count number of columns
n_cols <- ncol(resulttable1_df)

# Create and format flextable
ft <- flextable(resulttable1_df) |> 
  # Borders
  border_outer(part = "all") |> 
  border_inner(part = "all") |> 
  border_inner_h(part = "all") |> 
  border_inner_v(part = "all") |> 
  # Formatting
  bold(part = "header") |> 
  fontsize(size = 10, part = "all") |> 
  color(color = "black", part = "all") |> 
  # Width control
  set_table_properties(width = 1, layout = "autofit") |> 
  # Set relative column widths (adjust proportions as needed)
  width(width = rep(1, n_cols))  # Equal width for all columns

# Alternative for different column widths:
# width(width = c(2, rep(1, n_cols-1)))  # First column wider

# Display table
ft
```
Pembrolizumab has the highest number of reactions. The largest percentage of reactions are classified as "Other". These include reactions which do not belong to the other organ classes, such as myositis.

@@

For the disproportionality analysis, we need 4 different values:
a: Number of reports reporting both the drug and the adverse event. 
b: Number of reports reporting the drug but not the adverse event. 
c: Number of reports reporting the adverse event but not the drug. 
d: Number of reports reporting neither the drug nor the adverse event.

For PRR, the formula used is:
(a/(a+c)) / (b/(b+d))

For ROR:
(a/c)/(b/d)

For IC: 
log2((a+b+c+d)/(a+c)*(a+b)/n)

The following tables show the results from the disproportionality analysis.

```{r}
#| label: tbl-atezolizumab
#| tbl-cap: "Atezolizumab Reactions by Organ System"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(officer)

# Load and prepare the table
table_atezolizumab <- readRDS("../../results/tables/table_atezolizumab.rds") |>
  (\(x) x[-c(1, 2), ])()  # Remove first two rows using base R

# Create and format flextable
atezolizumab_table <- flextable(table_atezolizumab) |> 
  # Basic formatting
  bold(part = "header") |> 
  border(part = "all", border = officer::fp_border(color = "black", width = 1)) |> 
  # Text alignment
  align(align = "center", part = "header") |> 
  align(align = "left", part = "body") |> 
  # Cell padding
  padding(padding = 4, part = "all") |> 
  # Font settings
  fontsize(size = 10, part = "all") |> 
  # Width control
  set_table_properties(
    width = 1,                # 100% of available width
    layout = "autofit"        # Automatic column adjustment
  ) |> 
  # Column width fine-tuning (adjust values as needed)
  width(j = NULL, width = c(2, rep(1, ncol(table_atezolizumab)-1)))

# Display the table
atezolizumab_table
```

```{r}
#| label: tbl-avelumab
#| tbl-cap: "Avelumab Reactions by Organ System"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(officer)  # For fp_border()

# Load and prepare data
avelumab_data <- readRDS("../../results/tables/table_avelumab.rds")[-c(1, 2), ]

# Create and format flextable
avelumab_table <- flextable(avelumab_data) |> 
  # Formatting
  bold(part = "header") |> 
  # Borders
  border(part = "all", border = fp_border(color = "black", width = 1)) |> 
  # Width control
  set_table_properties(width = 1, layout = "autofit") |> 
  # Column widths (adjust values as needed)
  width(width = c(2, rep(1.2, ncol(avelumab_data)-1))) |> 
  # Additional formatting
  align(align = "center", part = "header") |> 
  padding(padding = 4, part = "all") |> 
  fontsize(size = 10, part = "all")

# Display table 
avelumab_table
```

```{r}
#| label: tbl-nivolumab
#| tbl-cap: "Nivolumab Reactions by Organ System"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(officer)  # Required for fp_border()

# Load and prepare data
nivolumab_data <- readRDS("../../results/tables/table_nivolumab.rds")[-c(1, 2), ]

# Create and format flextable
nivolumab_table <- flextable(nivolumab_data) |> 
  # Basic formatting
  bold(part = "header") |> 
  # Complete border styling
  border(part = "all", border = officer::fp_border(color = "black", width = 1)) |> 
  # Width and layout control
  set_table_properties(
    width = 1,                # Use 100% of available width
    layout = "autofit"        # Smart column adjustment
  ) |> 
  # Column width specification (adjust as needed)
  width(width = c(2.5, rep(1.5, ncol(nivolumab_data)-1))) |> 
  # Additional professional formatting
  align(align = "center", part = "header") |> 
  align(align = "left", part = "body") |> 
  padding(padding = 5, part = "all") |> 
  fontsize(size = 10, part = "all") |> 
  font(fontname = "Arial", part = "all")

# Display the table
nivolumab_table
```

```{r}
#| label: tbl-pembrolizumab
#| tbl-cap: "Pembrolizumab Reactions by Organ System"
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(officer)  # Required for fp_border()

# Load and prepare data
pembro_data <- readRDS("../../results/tables/table_pembrolizumab.rds")[-c(1, 2), ]

# Create and format flextable
pembro_table <- flextable(pembro_data) |> 
  bold(part = "header") |> 
  border(part = "all", border = fp_border(color = "black", width = 1)) |> 
  set_table_properties(width = 1, layout = "autofit") |> 
  width(width = c(2.2, rep(1.5, ncol(pembro_data)-1))) |> 
  align(align = "left", part = "body", j = 1) |> 
  align(align = "left", part = "body", j = 2:ncol(pembro_data)) |> 
  align(align = "center", part = "header") |> 
  padding(padding = 5, part = "all") |> 
  fontsize(size = 10, part = "all")

# Display table
pembro_table
```

The PRR and ROR when all irAEs are considered is greater than 1 for pembrolizumab (PRR: 1.8 (1.52, 2.14), ROR: 2.07 (1.69, 2.55)). Similarly, the IC is greater than 0 (0.36 (0.29, 0.44)). Thus, there is a safety signal associated with pembrolizumab for all irAEs.

When considering individual irAEs, pembrolizumab also has a safety signal for rash (PRR: 2.11 (1.17, 3.8), ROR: 2.14 (1.18, 3.9), IC: 0.44 (0.17, 0.71).

Atezolizumab has a safety signal for hyperthyroidism (PRR: 3.51 (1.07, 11.45), ROR: 3.53 (1.07, 11.61), IC:	1.1 (0.33, 1.87). There also may be a signal for nephritis (PRR: 3.65 (0.98, 13.56), ROR: 3.68 (0.98, 13.73), IC:	1.12 (0.29, 1.96), though the 95% CI for PRR and ROR is not greater than 1 (though very close to 1).

Similarly, avelumab may has a safety signal for hypothyroidism (PRR: 3.05 (0.98, 9.51), ROR:	3.08 (0.97, 9.75), IC:	1.32 (0.12, 2.52)).

No significant safety signals were found for nivolumab.

A random forest model was built to distinguish between serious and non-serious outcomes using age, sex, and ICI.
Inverse weighting was used to deal with the class imbalance.
The model was built using cross-validation.

```{r}
#| label: tbl-randomforest
#| tbl-cap: "Random Forest Evaluation Metrics"  # Removed "Table X" to prevent duplication
#| echo: FALSE
#| warning: FALSE
#| message: FALSE

library(flextable)
library(officer)

# Load and prepare data
rf_metrics <- readRDS("../../results/tables/randomforesttable.rds")

# Create professional flextable
flextable(rf_metrics) |> 
  # Basic formatting
  bold(part = "header") |> 
  border(part = "all", border = fp_border(color = "black", width = 1)) |> 
  # Number formatting
  colformat_double(digits = 3) |>  # Adjust decimal places as needed
  # Alignment
  align(align = "center", part = "header") |> 
  align(align = "right", part = "body", j = which(sapply(rf_metrics, is.numeric))) |> 
  # Layout
  set_table_properties(width = 1, layout = "autofit") |> 
  width(width = c(1.8, rep(1.2, ncol(rf_metrics)-1))) |>  # Adjust column widths
  # Visual enhancements
  bg(part = "header", bg = "#f2f2f2") |>  # Light gray header
  fontsize(size = 10, part = "all") |> 
  padding(padding = 4, part = "all")
```

We see that the accuracy is quite low (~25%). The model is not able to distinguish well between serious and non-serious cases, classifying most non-serious cases as serious. This issue arises due to the class imbalance in the data used to train the model (305 serious cases out of 365).
Advanced machine learning methods may be explored to overcome this problem. Some additional methods will be considered in part 5.

@@

In this study, the safety signals for the most commonly reported irAEs in clinical trials were assessed.
Safety signals for pembrolizumab included all irAEs as a whole, as well as a signal for rash.
Hyperthyroidism was a concern with atezolizumab, while nephritis may also be an issue.
Hypothyroidism could be of concern with avleumab use.
No specific signals were found with nivolumab.

@@

This study used data from the FAERS dashboard, and thus provides real-world evidence regarding the association of irAEs with ICI use in bladder cancer.
To my knowledge, this is the first study using FAERS data to assess this association.
However, the findings of this study must be considered in context of certain limitations.
Firstly, FAERS data has several limitations. The dashboard cannot provide causal information. 
This is a voluntary system. In the US, only drug manufacturers are mandated to reported adverse events. This means that all events are not reported.
Additionally, the reports may have duplicates, or may be incomplete. Efforts have been made in this study to remove the duplicates, but data completeness cannot be ensured.
Pembrolizumab was approved in 2014, while avelumab, nivolumab, and atezolizumab were initially approved in 2017, with additonal approvals in later years for other stages of bladder cancer.
As such, the larger number of reports associated with pembrolizumab may simple be due to the larger reporting time.
A future analysis with additional data may find different results to the one obtained using data until December 2024.

@@

Immune checkpoint inhibitor therapy are associated with immune-related adverse events (particularly rash, hypothyroidism, hyperthyroidism, and nephritis) in bladder cancer. Currently, no established guidelines exist to manage these adverse events.
There is a need to develop centralized guidelines and protocols for managing irAEs associated with ICI therapy.

*More details will be added in part 5 to the discussion section.*
